\section{List of publications}
\cvitem{}{A list of the 10 most important publications where I have been the main contributor is given below. The full list of publications can be found in the CV.}

\vspace{0.5cm}
\cvitem{\textbf{t\=tH(b\=b) and BSM t\=tb\=b}}{
Lead analyser for the t\=tH(b\=b), VLQ ($T \rightarrow Ht$) and stop ($\tilde{t}_2 \rightarrow \tilde{t}_1 H$) analyses. My t\=tH(b\=b) result was the single most sensitive analysis to t\=tH in Run 1. The VLQ analysis was the strongest one among the analyses entering the combination, and provided world-best limits at the time.
}
\begin{thebibliography}{10}
%\small
\makeatletter
\renewcommand\@biblabel[1]{}
\makeatother
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\expandafter\ifx\csname href\endcsname\relax
  \def\href#1#2{#2} \def\path#1{#1}\fi

\bibitem{HIGG-2013-27}
{ATLAS Collaboration}, {\em Search for the Standard Model Higgs boson produced in
  association with top quarks and decaying into \(b\bar{b}\) in \(pp\)
  collisions at \(\sqrt{s} = 8\,\text{TeV}\) with the ATLAS detector}, 
  \coloredLink{http://dx.doi.org/10.1140/epjc/s10052-015-3543-1}
  {Eur. Phys. J. C 75 (2015) 349}.


\bibitem{EXOT-2013-18}
{ATLAS Collaboration}, {\em Search for production of vector-like quark pairs and of
  four top quarks in the lepton-plus-jets final state in \(pp\) collisions at
  \(\sqrt{s} = 8\,\text{TeV}\) with the ATLAS detector}, 
  \coloredLink{http://dx.doi.org/10.1007/JHEP08(2015)105}
  {JHEP 08 (2015) 105}.

\bibitem{SUSY-2014-07}
{ATLAS Collaboration}, {\em ATLAS Run 1 searches for direct pair production of
  third-generation squarks at the Large Hadron Collider}, 
  \coloredLink{http://dx.doi.org/10.1140/epjc/s10052-015-3726-9}
  {Eur. Phys. J. C 75 (2015) 510}.
\end{thebibliography}


\vspace{0.5cm}
\cvitem{\textbf{Tile calorimeter}}{
Contributor to the characterisation of the Tile calorimeter timing performance and calibration, documented as part of the Tile Calorimeter paper.
}
\begin{thebibliography}{10}
%\small
\makeatletter
%\addtocounter{\@listctr}{3}
\renewcommand\@biblabel[1]{}
\makeatother
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\expandafter\ifx\csname href\endcsname\relax
  \def\href#1#2{#2} \def\path#1{#1}\fi

\bibitem{TCAL-2017-01}
{ATLAS Collaboration}, {\em Operation and performance of the ATLAS Tile Calorimeter
  in Run 1},
  \coloredLink{http://dx.doi.org/10.1140/epjc/s10052-018-6374-z}
  {Eur. Phys. J. C 78 (2018) 987}.
  
\end{thebibliography}


\vspace{0.5cm}
\cvitem{\textbf{RPC SUSY}}{
Main analyser, analysis contact and paper editor. 
The signal benchmarks, background estimation methods, and analysis strategy that I implemented in the analysis have continued being used for the publication with full Run 2 data, highlighting the robust work that went into this set of searches.
}
\begin{thebibliography}{10}
%\small
\makeatletter
%\addtocounter{\@listctr}{4}
\renewcommand\@biblabel[1]{}
\makeatother
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\expandafter\ifx\csname href\endcsname\relax
  \def\href#1#2{#2} \def\path#1{#1}\fi
  
\bibitem{SUSY-2015-02}
{ATLAS Collaboration}, {\em Search for top squarks in final states with one
  isolated lepton, jets, and missing transverse momentum in \(\sqrt{s} =
  13\,\text{TeV}\) \(pp\) collisions with the ATLAS detector},
  \coloredLink{http://dx.doi.org/10.1103/PhysRevD.94.052009}
  {Phys. Rev. D 94 (2016) 052009}.


\bibitem{SUSY-2016-16}
{ATLAS Collaboration}, {\em Search for top-squark pair production in final states
  with one lepton, jets, and missing transverse momentum using
  \(36\,\text{fb}^{-1}\) of \(\sqrt{s} = 13\,\text{TeV}\) \(pp\) collision data
  with the ATLAS detector}, 
  \coloredLink{http://dx.doi.org/10.1007/JHEP06(2018)108}
  {JHEP 06 (2018) 108}.
  
\end{thebibliography}

\vspace{0.5cm}
\cvitem{\textbf{RPV and long-lived SUSY}}{
Main analyser, analysis contact and paper editor. I developed from scratch fully new data-driven techniques to estimate backgrounds in previously-uncovered final states. The last result is the first LHC search to surpass the limits on higgsinos with RPV decays set by LEP. In a reinterpretation of existing results, I also demonstrated explicitly for the first time the good sensitivity of prompt searches to signals with long lifetime. 
}
\begin{thebibliography}{10}
%\small
\makeatletter
%\addtocounter{\@listctr}{6}
\renewcommand\@biblabel[1]{}
\makeatother
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\expandafter\ifx\csname href\endcsname\relax
  \def\href#1#2{#2} \def\path#1{#1}\fi

\bibitem{SUSY-2016-11}
{ATLAS Collaboration}, {\em Search for new phenomena in a lepton plus high jet
  multiplicity final state with the ATLAS experiment using \(\sqrt{s} =
  13\,\text{TeV}\) proton--proton collision data}, 
  \coloredLink{http://dx.doi.org/10.1007/JHEP09(2017)088}
  {JHEP 09 (2017) 088}.
  
  
\bibitem{ATLAS-CONF-2018-003}
{ATLAS Collaboration}, {\em Reinterpretation of searches for
  supersymmetry in models with variable \(R\)-parity-violating coupling
  strength and long-lived \(R\)-hadrons}, 
  \coloredLink{https://atlas.web.cern.ch/Atlas/GROUPS/PHYSICS/CONFNOTES/ATLAS-CONF-2018-003/}{ATLAS-CONF-2018-003}.  

\bibitem{SUSY-2019-04}
{ATLAS Collaboration}, {\em {Search for R-parity-violating supersymmetry in a
  final state containing leptons and many jets with the ATLAS experiment using
  \(\sqrt{s} = 13\,\text{TeV}\) proton--proton collision data}\/},
  \coloredLink{http://dx.doi.org/10.1140/epjc/s10052-021-09761-x}{Eur. Phys. J. C
  {81} (2021)  1023}.

\end{thebibliography}

\vspace{0.5cm}
\cvitem{\textbf{Trigger}}{
Editor of the trigger menu public notes documenting the content and evolution of the physics menu, including the special runs.
}
\begin{thebibliography}{10}
%\small
\makeatletter
%\addtocounter{\@listctr}{9}
\renewcommand\@biblabel[1]{}
\makeatother
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\expandafter\ifx\csname href\endcsname\relax
  \def\href#1#2{#2} \def\path#1{#1}\fi

\bibitem{ATL-DAQ-PUB-2019-001}
{ATLAS Collaboration}, {\em Trigger Menu
  in 2018}, \coloredLink{https://atlas.web.cern.ch/Atlas/GROUPS/PHYSICS/PUBNOTES/ATL-DAQ-PUB-2019-001/}{ATL-DAQ-PUB-2019-001}.  
\end{thebibliography}

