\section{Statement of research interest}
\cventry{\textbf{}}{}{}{}{
After the observation of the Higgs boson, one of the main priorities for Run II of the LHC is the exploration of the energy frontier. No significant excess has been observed so far with the current Run II dataset, and stringent limits have been set on simplified models. 
The motivation for some form of new physics is still strong but it is obvious that it is not manifested in the vanilla signatures that were the main focus of attention. 
At this stage two different approaches can and should be pursued. One on side, searches in final states with low cross section or challenging signatures will become more relevant with the growing dataset. On the other side, precision measurements can provide a ground where deviations from the SM prediction can shed further light on the presence or absence of new physics.
}{}{}
% Higgs to WW
\cventry{\textbf{H $\bm{\rightarrow}$ WW$^*$}}{}{}{}{
%\cventry{\textbf{}}{}{}{}{
The discovery of the Higgs boson was a milestone in the LHC program, and although so far all the measurements are compatible with the SM prediction, most of its properties have not been measured yet. Precise measurements of its properties, and in particular differential distributions, are of key importance. The decay channel $H \rightarrow WW^*$ was the most sensitive one in Run I, with a comparable contribution from statistics and systematic uncertainties. Careful work will be needed to improve the systematic uncertainties and benefit from the increased dataset. This is an area where I would like to contribute, and where dedicated and detailed work can make a large impact towards improved inclusive and differential measurements.
}{}{}
% Higgsinos
\cventry{\textbf{Higgsinos}}{}{}{}{
%\cventry{\textbf{}}{}{}{}{
One of the areas where the increased dataset will make great difference is electroweak supersymmetry. In particular searches for higgsinos, which are motivated by naturalness arguments, will be feasible thanks to the dedicated triggers and the improvements towards soft lepton reconstruction. The very low cross section and signal to background ratio will require an excellent understanding of the detector performance and modeling systematics in order to surpass LEP limits.
}{}{}
% VBF and VBS
\cventry{\textbf{VBF and VBS}}{}{}{}{
%\cventry{\textbf{}}{}{}{}{
In both of the mentioned analyses, the VBF topology can be exploited to further improve the sensitivity. In Run I the combination of ATLAS and CMS measurements was required to achieve the observation of Higgs production via vector boson fusion. In the search for higgsinos, the inclusion of several production modes will be needed to reach good sensitivity. However, the increased pileup conditions in the coming years will make this final state even more challenging. 
In the longer term, the identification of the VBF topology will also be a key ingredient for measurements of vector boson scattering. The measurement of VBS is a fundamental test to verify whether the VV cross section regularization is performed only by the Higgs boson or by other particles.
Given the multiple applications, I would like to work towards the improvement of pileup rejection in forward jets, and the development of more sophisticated techniques towards VBF tagging. The improvement in VBF identification will directly improve the aforementioned analyses, while the improvements in pileup rejection could benefit the whole collaboration. 
}{}{}
% Upgrade and trigger?
%\cventry{\textbf{}}{}{}{}{
%}{}{}
%%This is not related to future but matches if I had described my past experience
%\cventry{\textbf{}}{}{}{}{
%In summary, I believe my training, experience and contribution to different analyses have prepared me to be an effective postdoctoral researcher. 
%%Your institution, hosting one of the largest and most prestigious ATLAS groups, would be the ideal place to continue my research.
%I would be happy to answer any further questions you may have, or provide any supplementary material you may need. I thank you very much for your consideration of my candidacy and sincerely look forward to hearing from you.}{}{}
