\chapter*{Acknowledgements}
\markboth{Acknowledgements}{}
    \label{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

Although there is only one name in bold font in the title page, the list of people that have contributed in some way to this thesis is incredibly long. 

First of all I want to thank my supervisor Aurelio for all the hard work, support and guidance. 
The work towards this thesis has been incredibly rewarding, and I learned a great amount about the challenges of a physics analysis through
his optimistic and passionate scientific approach.
A big thank you also to the whole IFAE group, with which I had the pleasure of sharing these years, in particular Mario, Martine, Matteo, Ram\'{o}n, Pilar and Imma.
And although it has been some time, a big thank you also to Alfredo Valcarce, who first showed me the wonders of particle physics and research.

This adventure started four years ago and I was really lucky to meet some incredible people along the way. 
Roger, Garo\'{e} and Clara, we started this together as total strangers and we ended up living together. From Catan to music club, it has been some great years and I'm sure there are more to come. 

I also want to thank warmly all the people I worked with at CERN, especially Stefan, Valerio and Tamara. Sharing sleepless work nights, kebab-football, ntuple debugging and billiard made the approval process even fun, and the subsequent workshop-holidays even more!
A big hug also to Mirko, I feel always flattered when I'm called ``Python guru'' although I'm definitively not. It was great to work with you and the Italian dinners were really amazing, although the wine could have been better (now it is your responsibility to tell the truth).

I also wanted to thank all my gurus, which I bombarded with questions during my first years, and which were answered really kindly. 
Big thanks to  Clement, Antonella, Francesco, Paolo, Jordi and Volker. Your wise words still resonate in the office: ``array caca, vector mola, visca vim''.

Of course not everybody was new, and I was always supported and encouraged by my old friends in Salamanca and the new ones in Geneva. A very special mention to
Cayetano and Molina here, for the great times we had all around the world: next destination Netherlands.

A big thank you also to my parents and my brother, which have followed every step towards this thesis with great enthusiasm. After living abroad for so long, every time I'm back in Salamanca it still feels like being back home.

Finally, the biggest thank you of all goes to Nani, who supported and encouraged me throughout the good and the bad times. You gave me the strength to finish the writing in no time and made these years an amazing time. And I promise, the future is going to be even better.
